Still Missing a Cool Title

### 2006-05-31 talk/dls2006/paper.tex
The \ss sign.
use eps figures

\numberofauthors{2}
\author{
\alignauthor Armin Rigo\\
       \affaddr{Heinrich-Heine-Universität Düsseldorf}\\
       \affaddr{Institut für Informatik}\\ 
       \affaddr{Universitätsstraße 1}\\
       \affaddr{D-40225 Düsseldorf}\\
       \affaddr{Deutschland}\\
       \email{arigo@tunes.org}
\alignauthor Samuele Pedroni\\
       \affaddr{AB Strakt}\\
       \affaddr{Norra Ågatan 10A}\\
       \affaddr{416 64  Göteborg}\\
       \affaddr{Sweden}\\
       \email{pedronis@strakt.com}
}
\date{31 May 2006}
\maketitle

@@

\begin{figure}
\centering
\includegraphics[scale=0.667]{image/typesystems.pdf}
\caption{type systems; the arrows are transformations.}
\label{fig_typesystems}
\end{figure}

@@

We mitigate the potential efficiency problem by wise choices and
compromises for the domain used; the foremost example of this is that
our RPython type inference performs almost no polymorphic specialization
of functions.  Another example is that unlike some schemes which follow
exact sets of concrete run-time classes, we only propagate a single
superclass per variable: the most precise common parent class.  This
gives enough precision for our code generation purposes.

@@

\begin{figure*}
\centering
\includegraphics[scale=0.75]{image/flowlattice.pdf}
\caption{The lattice order of the flow object space}
\label{flowlattice}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[scale=0.75]{image/lattice1.pdf}
\caption{The overall lattice}
\label{latticeoverall}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[scale=0.75]{image/lattice2.pdf}
\caption{The part about instances and nullable instances, assuming a
  simple class hierarchy with only two direct subclasses of
  \texttt{object}.}
\label{latticedetail}
\end{figure*}

>>>>

\numberofauthors{2}
\author{
\alignauthor Armin Rigo\\
       \affaddr{Heinrich-Heine-Universität Düsseldorf}\\
       \affaddr{Institut für Informatik}\\ 
       \affaddr{Universitätsstra{\ss}e 1}\\
       \affaddr{D-40225 Düsseldorf}\\
       \affaddr{Deutschland}\\
       \email{arigo@tunes.org}
\alignauthor Samuele Pedroni\\
       \affaddr{AB Strakt}\\
       \affaddr{Norra Ågatan 10A}\\
       \affaddr{416 64  Göteborg}\\
       \affaddr{Sweden}\\
       \email{pedronis@strakt.com}
}
\date{31 May 2006}
\maketitle

@@

\begin{figure}
\centering
\epsfig{file=image/typesystems.eps, scale=0.667}
\caption{type systems; the arrows are transformations.}
\label{fig_typesystems}
\end{figure}

@@

We mitigate the potential efficiency problem by wise choices and
compromises for the domain used; the foremost example of this is that
our RPython type inference performs almost no automatic specialization
of functions in the presence of polymorphic arguments.  Another
example is that unlike some schemes which follow exact sets of
concrete run-time classes, we only propagate a single superclass per
variable: the most precise common parent class.  This gives enough
precision for our code generation purposes.

@@

\begin{figure*}
\centering
\epsfig{file=image/flowlattice.eps, scale=0.65}
\caption{The lattice order of the flow object space}
\label{flowlattice}
\end{figure*}

@@

\begin{figure*}
\centering
\epsfig{file=image/lattice1.eps, scale=0.75}
\caption{The overall lattice}
\label{latticeoverall}
\end{figure*}

\begin{figure*}
\centering
\epsfig{file=image/lattice2.eps, scale=0.75}
\caption{The part about instances and nullable instances, assuming a
  simple class hierarchy with only two direct subclasses of
  \texttt{object}.}
\label{latticedetail}
\end{figure*}
